Predictors of frog survival following translocations - supplemental analyses

### 2023-03-14 code/translocation_survival_analysis.Rmd
Rearrange load-libraries code chunks
Minor updates to analysis code

@@

### Load packages

```{r}
library(tidyverse)
library(brms)
library(rstanarm)
library(bayesplot)
library(tidybayes)
library(loo)
library(broom.mixed)
library(janitor)
library(patchwork)

@@

```{r}
cond_effects_plot <- (p_snowt1 | p_elev) / (p_donor | p_sex)
```

>>>>

## Load packages

```{r}
library(tidyverse)
library(brms)
library(rstanarm)
library(bayesplot)
library(tidybayes)
library(loo)
library(broom.mixed)
library(janitor)
library(patchwork)
library(lubridate)

@@

@@

```{r}
cond_effects_plot <- (p_snowt1 | p_elev) / (p_donor | p_sex)
cond_effects_plot
```

### 2023-03-14 code/translocation_survival_analysis_suppl.Rmd
Minor updates to analysis code

```{r}
library(tidyverse)
library(brms)
library(rstanarm)
library(bayesplot)
library(tidybayes)
library(loo)
library(broom.mixed)
library(janitor)

@@

### Load additional libraries

```{r}
library(RPostgreSQL)
library(lubridate)
```

@@

### Load packages

```{r}
library(RPostgreSQL)
library(lubridate)
library(dplyr)
library(magrittr)
library(readr)
```

@@

-   Use 2nd chunk when connecting via SSH.

@@

```{r}
con = dbConnect(dbDriver("PostgreSQL"),
                host = "localhost",
                port = 15432,
                dbname = Sys.getenv("dbname"), 
                user = rstudioapi::askForPassword("user name"),
                password = rstudioapi::askForPassword("password")
                )
```

>>>>

```{r}
library(RPostgreSQL)
library(tidyverse)
library(lubridate)
library(brms)
library(rstanarm)
library(bayesplot)
library(tidybayes)
library(loo)
library(broom.mixed)
library(janitor)

@@

@@

@@

@@
